Model Recognition as Planning

### 2019-02-08 doc/icaps-19/submitted/model-recognition.tex
new folders for preparing the icaps19 camera ready

\author{\#92}
% Commented for blind submission
%\author{Diego Aineto \and Sergio Jim\'enez\and Eva Onaindia\\
%{\scriptsize Departamento de Sistemas Inform\'aticos y Computaci\'on}\\
%{\scriptsize Universitat Polit\`ecnica de Val\`encia.}\\
%{\scriptsize Camino de Vera s/n. 46022 Valencia, Spain}\\
%{\scriptsize \{dieaigar,serjice,onaindia\}@dsic.upv.es}
%\And Miquel Ram\'irez\\
%{\scriptsize School of Computing and Information Systems}\\
%{\scriptsize The University of Melbourne}\\
%{\scriptsize Melbourne, Victoria. Australia}\\
%{\scriptsize miquel.ramirez@nimelb.edu.au}}

>>>>

%\author{\#92}
% Commented for blind submission
\author{Diego Aineto \and Sergio Jim\'enez\and Eva Onaindia\\
{\scriptsize Departamento de Sistemas Inform\'aticos y Computaci\'on}\\
{\scriptsize Universitat Polit\`ecnica de Val\`encia.}\\
{\scriptsize Camino de Vera s/n. 46022 Valencia, Spain}\\
{\scriptsize \{dieaigar,serjice,onaindia\}@dsic.upv.es}
\And Miquel Ram\'irez\\
{\scriptsize School of Computing and Information Systems}\\
{\scriptsize The University of Melbourne}\\
{\scriptsize Melbourne, Victoria. Australia}\\
{\scriptsize miquel.ramirez@nimelb.edu.au}}
